Locating Data Flow Anomaly With Statistical Distance

### 2017-09-17 Paper/DataAnomaly/paper.tex
Write Abstract

	\begin{abstract}
		[abstract]
	\end{abstract}

>>>>

	\begin{abstract}
		Hackers can infiltrate networks via any attack vector, find their way into databases and applications. Not only can they steal chunks of data and hold them for ransom, but also alter key information contained in those systems, setting up traps hard to discover and causing damages unlikely to recover. Although the influence of data altering is not significant in single data record, the change can be observed and detect in a collective scale.
		In this paper, we present a dynamic collective anomaly detection technique based on statistical distance. The technique extracts distribution similarities among data collections, reducing collective anomalies into point anomalies. It dynamically calculate metrics which is adaptive to the slightly evolving features. This technique provides a basic solution where several components can be replaced by other scenario specific ones, further improving the performance of detection.
		To illustrate details of the technique and explore its efficiency, we applied the algorithm into a real world problem of click farming detection against malicious online sellers. The evaluation shows that the technique maps normal and anomalous data collections into two distinct clusters, yielding efficient classifiers. And those classifiers are sensitive enough to a much smaller magnitude of manipulation compared with real world malicious behaviours.
	\end{abstract}
